### 2021-11-07 README.Rmd
changes in readme
Updated readme with ecdf and dotplot examples

The next example uses the iris dataset, with matrices `x` and `y` as shown below. The `Sepal.Length` is plotted against `Sepal.Width` and the `Petal.Length` is plotted against `Petal.Width`. Therefore the groups 'Column 1' and 'Column 2' can be interpreted as 'Sepal' and 'Petal' respectively. To make the plot more meaningful, we can add the legend label and axis names by `legend_label`, `xlab` and `ylab`.

@@

Similar to density, violin and box plots, histograms too accept a single matrix or data frame input and groups the plot using its columns. The histogram in the following example uses a matrix of 4 columns, and therefore groups the plots based on these 4 columns. The plot is also faceted by group.

@@

```{r histogram}
# matrix X
x <- (iris[, 1:4])

@@

>>>>

The next example uses the iris dataset, with matrices `x` and `y` as shown below. The `Sepal.Length` is plotted against `Sepal.Width` and the `Petal.Length` is plotted against `Petal.Width`. Therefore the groups 'Column 1' and 'Column 2' can be interpreted as 'Sepal' and 'Petal' respectively. To make the plot more meaningful, we can further add the legend label and axis names by `legend_label`, `xlab` and `ylab`.

@@

Dotplots too accept a single matrix input and plots the distribution of each of its columns.

The next example uses the `plot_type = "dotplot"` to visualise the distribution of the data, and also customizes the position of the legend using a `ggplot` theme as well.

```{r dotplot}
# matrix x
x <- (iris[, 1:2])

ggmatplot(x,
  plot_type = "dotplot",
  color = c("#00AFBB", "#E7B800"),
  xlab = "", ylab = ""
) +
  theme(legend.position = "bottom")
```

Similar to density, violin, dotplots, and box plots, histograms too accept a single matrix or data frame input and groups the plot using its columns. The histogram in the following example uses a matrix of 4 columns, and therefore groups the plots based on these 4 columns. The plot is also faceted by group.

@@

```{r histogram}
# matrix x
x <- (iris[, 1:4])

@@

The next example is of the `plot_type = ecdf`, and also uses a single matrix input to plot out the empirical cumulative distributions of the columns of the matrix individually.

```{r ecdf}
# matrix x
x <- (iris[, 1:4])

ggmatplot(x,
  plot_type = "ecdf",
  xlab = "Group",
  size = 1
) +
  theme_minimal()
```
